A community-maintained standard library of population genetic models

### 2020-04-30 popSimManu.tex

>>>>

The possibility for error and the importance of careful qualty control
was inadvertantly illustrated during our own development process:
during the final revisions of this paper, we noticed that the 
OutOfAfrica\_3G09 model \citep{gutenkunst2009inferring}
had not in fact gone through the QC process.
Then, the QC process revealed that not only was our implementation
slightly wrong---migration rates had not been set to zero to the European population in the longest-ago time period
when there should have only been a single population.
This error was in fact propagated from the \texttt{msprime} documentation.
